**Density Dependence**

### 2023-02-28 Rmd/report mac.Rmd
report.R & report Mac.Rmd

# fig_nums(name    = "section2_fig", caption = "section2_fig", level = 1, display = FALSE)
# tab_nums(name    = "section2_tab", caption = "section2_tab", level = 1, display = FALSE)

@@

knitr::include_graphics(path=file.path(figuresdir, paste(mystk, "waa.jpg", sep="_")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste(mystk, "mat.jpg", sep="_")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste(mystk, "m.jpg", sep="_")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste(mystk, "dd_waa.jpg", sep="_")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste(mystk, "gamm.jpg", sep="_")))

@@

cat(readLines(file.path(tablesdir, paste(mystk, "gamm summary.txt", sep="_"))), sep = '\n')

@@

cat(readLines(file.path(tablesdir, paste(mystk, "gamm coefficients.txt", sep="_"))), sep = '\n')

@@

knitr::include_graphics(path=file.path(figuresdir, paste(mystk, "lm_waa.jpg", sep="_")))

@@

cat(readLines(file.path(tablesdir, paste(mystk, "lm summary.txt", sep="_"))), sep = '\n')

@@

knitr::include_graphics(path=file.path(figuresdir, paste(mystk, "dd_mat.jpg", sep="_")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste(mystk, "mat_ogive.jpg", sep="_")))

@@

@@

knitr::include_graphics(path=file.path(figuresdir, paste0(mystk,"_sim_dd_mass.jpg")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste0(mystk,"_sim_dd_maturity.jpg")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste0(mystk,"_sim_dd_m.jpg")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste0(mystk,"_eq_yield.jpg")))

@@

@@

knitr::include_graphics(path=file.path(figuresdir, paste0(mystk,"_comparing_assessments.jpg")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste0(mystk,"_VPADDM_4panels.jpg")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste0(mystk,"_VPADDMM_4panels.jpg")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste0(mystk,"_VPADDMMM_4panels.jpg")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste0(mystk,"_comparing_dd.jpg")))
```

@@

>>>>

# fig_nums(name    = "section2_fig", caption = "section2_fig", level = 1, display = FALSE)
# tab_nums(name    = "section2_tab", caption = "section2_tab", level = 1, display = FALSE)
section <- "02"

@@

knitr::include_graphics(path=file.path(figuresdir, paste(section, mystk, "waa.jpg", sep="_")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste(section,mystk, "mat.jpg", sep="_")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste(section,mystk, "m.jpg", sep="_")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste(section,mystk, "dd_waa.jpg", sep="_")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste(section,mystk, "gamm.jpg", sep="_")))

@@

cat(readLines(file.path(tablesdir, paste(section,mystk, "gamm summary.txt", sep="_"))), sep = '\n')

@@

cat(readLines(file.path(tablesdir, paste(section,mystk, "gamm coefficients.txt", sep="_"))), sep = '\n')

@@

knitr::include_graphics(path=file.path(figuresdir, paste(section,mystk, "lm_waa.jpg", sep="_")))

@@

cat(readLines(file.path(tablesdir, paste(section,mystk, "lm summary.txt", sep="_"))), sep = '\n')

@@

knitr::include_graphics(path=file.path(figuresdir, paste(section,mystk, "dd_mat.jpg", sep="_")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste(section,mystk, "mat_ogive.jpg", sep="_")))

@@

section <- "03"

@@

knitr::include_graphics(path=file.path(figuresdir, paste(section,mystk,"sim_dd_mass.jpg", sep="_")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste(section,mystk,"sim_dd_maturity.jpg",sep="_")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste(section,mystk,"sim_dd_m.jpg", sep="_")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste(section,mystk,"eq_yield.jpg",sep="_")))

@@

section <- "04"

@@

knitr::include_graphics(path=file.path(figuresdir, paste(section,mystk,"comparing_assessments.jpg",sep="_")))

@@

knitr::include_graphics(path=file.path(figuresdir, 
                                       paste(section,mystk,"VPADDM_4panels.jpg", sep="_")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste(section,mystk,"VPADDMM_4panels.jpg",sep="_")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste(section,mystk,"VPADDMMM_4panels.jpg",sep="_")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste(section,mystk,"comparing_dd.jpg",sep="_")))
```

@@

section <- "05"
